Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-11 paper-plan/paper-plan.tex
Hindsight FF-Replan + typos

\section{Problem formulation}
\begin{itemize}
	\item Summarize shortcomings of the previous solutions
	\item Describe the planning problem
	\item Argument the choice for 2 current papers to analyze
	\item Define how we would like to test the planning algorithms in a domain by our choice
\end{itemize}

From the related literature we identify some problems.

@@

\section{Empirical evalution}

@@

\begin{itemize}
	\item Conclude on the succes of the 2 approaches
	\item Conclude the work done in the paper
	\item Hint to some future work developments
\end{itemize}

>>>>

\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}

Hindsight optimization is an online technique that evaluates one-step-reachable
states by sampling future outcomes to generate multiple non-stationary planning
problems which are deterministic and can be used using search. It re-interprets
FF-Replan's~\ref{FFReplan} strategy randomly generating a set of non-stationary
determinized problems and combining their solutions.

\subsection{}

\section{Problem formulation}

\begin{itemize}
	\item Summarize shortcomings of the previous solutions
	\item Describe the planning problem
	\item Argument the choice for 2 current papers to analyze
	\item Define how we would like to test the planning algorithms in a domain by our choice
\end{itemize}

@@

\section{Empirical evaluation}

@@

\begin{itemize}
	\item Conclude on the success of the 2 approaches
	\item Conclude the work done in the paper
	\item Hint to some future work developments
\end{itemize}

\section{Some papers}
